Finite dimensional Lie algebras

### 2010-03-16 AffineLieAlgebras/SchemePrograms/LiterateLie.tex
Minor fixes

So we need just two following general functions:
\nwenddocs{}\nwbegincode{13}\sublabel{NW1VK18x-10zTlp-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-10zTlp-1}}}\moddef{Functions for root systems .scm~{\nwtagstyle{}\subpageref{NW1VK18x-10zTlp-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
(define (co-root r)
  (div (mul 2 r) (prod r r)))

(define (reflect weight root)
  (sub weight (mul (prod weight (co-root root)) root)))
\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{14}\nwdocspar
Here {\it co-root} $\alpha^{\vee}$ is the element of the dual space $(\mathfrak{h}^*)^*$ which is identified with $\mathfrak{h}^*\approx \mathfrak{h}$ since we have scalar product on $\mathfrak{h}$.

Now we can implement wide range of root system related methods of {\Tt{}semisimple-lie-algebra\nwendquote} class
\nwenddocs{}\nwbegincode{15}\sublabel{NW1VK18x-1H68wy-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{\relax}{NW1VK18x-1H68wy-2}\nwenddeflinemarkup
`(simple-co-roots ,(lambda (self)
              (map co-root (send self 'simple-roots))))
\nwalsodefined{\\{NW1VK18x-1H68wy-2}\\{NW1VK18x-1H68wy-3}\\{NW1VK18x-1H68wy-4}\\{NW1VK18x-1H68wy-5}\\{NW1VK18x-1H68wy-6}}\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{16}\nwdocspar
\begin{Def}
  {\bf Cartan matrix} with the elements
  \begin{equation}
    \label{eq:7}
    a_{ij}=(\alpha_i,\alpha_j^{\vee})=\frac{2(\alpha_i,\alpha_j)}{(\alpha_j,\alpha_j)}
  \end{equation}
  completely determines the set of simple roots and is useful for the classification and compact description of Lie algebras.
\end{Def}
\nwenddocs{}\nwbegincode{17}\sublabel{NW1VK18x-1H68wy-2}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-2}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-1}{NW1VK18x-1H68wy-3}\nwenddeflinemarkup
`(cartan-matrix
  ,(lambda (self)
     (map (lambda (a)
            (map (lambda (av) (prod a av)) (send self 'simple-co-roots)))
         (send self 'simple-roots))))
\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{18}\nwdocspar
We have already introduced Weyl group of reflections \ref{weyl-group-def}, now we implement procedure which constructs the union of Weyl group orbits of the set of weights.
\nwenddocs{}\nwbegincode{19}\sublabel{NW1VK18x-1H68wy-3}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-3}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-2}{NW1VK18x-1H68wy-4}\nwenddeflinemarkup
`(orbit ,
  (lambda (self weights)
    (let ((addon 
           (filter (lambda (x) (not (element-of-set? x weights)))
                   (fold-right union-set '() 
                               (map (lambda (w)
                                      (map
                                       (lambda (x) (reflect w x))
                                       (send self 'simple-roots)))
                                    weights)))))
      (if (null? addon)
          weights
          (send self 'orbit (union-set weights addon) )))))
\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{20}\nwdocspar
\begin{Def}
  {\bf Fundamental weights} form a basis $w_1,\dots,w_r$ dual to the basis of simple co-roots $\alpha_1^{\vee},\dots,\alpha_r^{\vee}$.
\end{Def}
\nwenddocs{}\nwbegincode{21}\sublabel{NW1VK18x-1H68wy-4}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-4}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-3}{NW1VK18x-1H68wy-5}\nwenddeflinemarkup
`(fundamental-weights
  ,(lambda (self)
     (map (lambda (x)
            (sum (map-n (lambda (y z) (mul y z)) x (send self 'simple-roots))))
          (matrix-inverse (send self 'cartan-matrix)))))
\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{22}\nwdocspar
{\bf Weyl vector} $\rho=\sum_i w_i=\frac{1}{2}\sum_{\alpha\in \Delta^{+}}\alpha$.
\nwenddocs{}\nwbegincode{23}\sublabel{NW1VK18x-1H68wy-5}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-5}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-4}{NW1VK18x-1H68wy-6}\nwenddeflinemarkup
`(rho ,(lambda (self)
         (sum (send self 'fundamental-weights))))

@@

\nwenddocs{}\nwbegincode{31}\sublabel{NW1VK18x-2w9Axe-2}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-2}}}\moddef{Representations .scm~{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwprevnextdefs{NW1VK18x-2w9Axe-1}{\relax}\nwenddeflinemarkup
(class 'highest-weight-representation 'representation
       '(highest-weight ())
       \LA{}Anomalous weights computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}\RA{}
       \LA{}Weight multiplicities computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}\RA{})
`(multiplicity , (lambda (self weight)
\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{32}\nwdocspar
We use the recurrent method of calculation of weight multiplicities described in \cite{lyakhovsky1996rra}, \cite{kulish4sfa}. Weight multiplicities are determined using the set of anomalous points, which is constructed by the code below.
\nwenddocs{}\nwbegincode{33}\sublabel{NW1VK18x-1y2eh2-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}}\moddef{Anomalous weights computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2w9Axe-2}}\nwenddeflinemarkup
       `(anomalous-weights , 
         (lambda (self)
           (let* ((algebra (send self 'lie-algebra))
                  (rho (send algebra 'rho)))
             (map (lambda (x)
                    (sub x rho))
                  (send algebra 'orbit (add (send self 'highest-weight) rho))))))
\nwused{\\{NW1VK18x-2w9Axe-2}}\nwendcode{}\nwbegindocs{34}\nwdocspar

\nwenddocs{}\nwbegincode{35}\sublabel{NW1VK18x-46EOV9-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}}\moddef{Weight multiplicities computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2w9Axe-2}}\nwenddeflinemarkup

@@

\nwused{\\{NW1VK18x-2tcrGt-1}}\nwendcode{}

\nwixlogsorted{c}{{Anomalous weights computation .scm}{NW1VK18x-1y2eh2-1}{\nwixu{NW1VK18x-2w9Axe-2}\nwixd{NW1VK18x-1y2eh2-1}}}%
\nwixlogsorted{c}{{Commutative algebra .scm}{NW1VK18x-I1QOi-1}{\nwixd{NW1VK18x-I1QOi-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Functions for root systems .scm}{NW1VK18x-10zTlp-1}{\nwixd{NW1VK18x-10zTlp-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{library.scm}{NW1VK18x-15DMjX-1}{\nwixd{NW1VK18x-15DMjX-1}}}%
\nwixlogsorted{c}{{Lie algebra class .scm}{NW1VK18x-4dzmez-1}{\nwixd{NW1VK18x-4dzmez-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Lie algebra methods .scm}{NW1VK18x-4X6QTQ-1}{\nwixu{NW1VK18x-4dzmez-1}\nwixd{NW1VK18x-4X6QTQ-1}}}%
\nwixlogsorted{c}{{lie-algebra.scm}{NW1VK18x-3yKaW-1}{\nwixd{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{LispMe Objects .scm}{NW1VK18x-26RKW4-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-26RKW4-1}}}%
\nwixlogsorted{c}{{Matrix inverse .scm}{NW1VK18x-1qnsIb-1}{\nwixu{NW1VK18x-2tcrGt-1}\nwixd{NW1VK18x-1qnsIb-1}}}%
\nwixlogsorted{c}{{Representations .scm}{NW1VK18x-2w9Axe-1}{\nwixd{NW1VK18x-2w9Axe-1}\nwixd{NW1VK18x-2w9Axe-2}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Root system methods .scm}{NW1VK18x-1H68wy-1}{\nwixu{NW1VK18x-1pDr9o-1}\nwixd{NW1VK18x-1H68wy-1}\nwixd{NW1VK18x-1H68wy-2}\nwixd{NW1VK18x-1H68wy-3}\nwixd{NW1VK18x-1H68wy-4}\nwixd{NW1VK18x-1H68wy-5}\nwixd{NW1VK18x-1H68wy-6}}}%
\nwixlogsorted{c}{{Semi-standard Scheme procedures .scm}{NW1VK18x-16zbNk-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-16zbNk-1}}}%
\nwixlogsorted{c}{{Semisimple Lie algebra .scm}{NW1VK18x-1QMleH-1}{\nwixd{NW1VK18x-1QMleH-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Semisimple Lie algebra methods .scm}{NW1VK18x-1pDr9o-1}{\nwixu{NW1VK18x-1QMleH-1}\nwixd{NW1VK18x-1pDr9o-1}}}%
\nwixlogsorted{c}{{Sets .scm}{NW1VK18x-3j9Egk-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-3j9Egk-1}}}%
\nwixlogsorted{c}{{Simple Lie algebras .scm}{NW1VK18x-379yCw-1}{\nwixd{NW1VK18x-379yCw-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Vector and matrix tools .scm}{NW1VK18x-2tcrGt-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-2tcrGt-1}}}%
\nwixlogsorted{c}{{Vector operations .scm}{NW1VK18x-14pT7v-1}{\nwixu{NW1VK18x-2tcrGt-1}\nwixd{NW1VK18x-14pT7v-1}}}%
\nwixlogsorted{c}{{Weight multiplicities computation .scm}{NW1VK18x-46EOV9-1}{\nwixu{NW1VK18x-2w9Axe-2}\nwixd{NW1VK18x-46EOV9-1}}}%
\nwbegindocs{53}\nwdocspar

\bibliography{LiterateLie}{}
\bibliographystyle{utphys}

>>>>

Also sometimes we need to know the determinant of Weyl group element and we can take it into account using the following version of the {\Tt{}reflect\nwendquote} function, called {\Tt{}reflect-with-eps\nwendquote}.

\nwenddocs{}\nwbegincode{13}\sublabel{NW1VK18x-10zTlp-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-10zTlp-1}}}\moddef{Functions for root systems .scm~{\nwtagstyle{}\subpageref{NW1VK18x-10zTlp-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
(define (co-root r)
  (div (mul 2 r) (prod r r)))

(define (reflect weight root)
  (sub weight (mul (prod weight (co-root root)) root)))

(define (reflect-with-eps weight root)
  (if (or (null? (cdr weight))
          (pair? (cdr weight)))
      (let ((v (reflect weight root)))
        (cons v (if (equal? weight v) 1 -1)))
      (let ((v (reflect (car weight) root)))
        (cons v (if (equal? (car weight) v) (cdr weight) (- (cdr weight)))))))

(define (eps weight)
  (if (or (null? (cdr weight))
          (pair? (cdr weight)))
      1
      (cdr weight)))

(define (no-eps weight)
  (if (or (null? (cdr weight))
          (pair? (cdr weight)))
      weight
      (car weight)))
\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{14}\nwdocspar
Here {\it co-root} $\alpha^{\vee}$ is the element of the dual space $(\mathfrak{h}^*)^*$ which is identified with $\mathfrak{h}^*\approx \mathfrak{h}$ since we have scalar product on $\mathfrak{h}$.

Now we can implement wide range of root system related methods of {\Tt{}semisimple-lie-algebra\nwendquote} class
\nwenddocs{}\nwbegincode{15}\sublabel{NW1VK18x-1H68wy-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{\relax}{NW1VK18x-1H68wy-2}\nwenddeflinemarkup
`(simple-co-roots ,(lambda (self)
              (map co-root (send self 'simple-roots))))
\nwalsodefined{\\{NW1VK18x-1H68wy-2}\\{NW1VK18x-1H68wy-3}\\{NW1VK18x-1H68wy-4}\\{NW1VK18x-1H68wy-5}\\{NW1VK18x-1H68wy-6}}\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{16}\nwdocspar
\begin{Def}
  {\bf Cartan matrix} with the elements
  \begin{equation}
    \label{eq:7}
    a_{ij}=(\alpha_i,\alpha_j^{\vee})=\frac{2(\alpha_i,\alpha_j)}{(\alpha_j,\alpha_j)}
  \end{equation}
  completely determines the set of simple roots and is useful for the classification and compact description of Lie algebras.
\end{Def}
\nwenddocs{}\nwbegincode{17}\sublabel{NW1VK18x-1H68wy-2}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-2}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-1}{NW1VK18x-1H68wy-3}\nwenddeflinemarkup
`(cartan-matrix
  ,(lambda (self)
     (map (lambda (a)
            (map (lambda (av) (prod a av)) (send self 'simple-co-roots)))
         (send self 'simple-roots))))
\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{18}\nwdocspar
We have already introduced Weyl group of reflections \ref{weyl-group-def}, now we implement procedure which constructs the union of Weyl group orbits of the set of weights.
\nwenddocs{}\nwbegincode{19}\sublabel{NW1VK18x-1H68wy-3}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-3}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-2}{NW1VK18x-1H68wy-4}\nwenddeflinemarkup
`(general-orbit , (lambda (self weights reflect)
    (let ((addon 
           (filter (lambda (x) (not (element-of-set? x weights)))
                   (fold-right union-set '() 
                               (map (lambda (w)
                                      (map
                                       (lambda (x) (reflect w x))
                                       (send self 'simple-roots)))
                                    weights)))))
      (if (null? addon)
          weights
          (send self 'general-orbit (union-set weights addon) reflect )))))

`(orbit ,
  (lambda (self weights)
    (send self 'general-orbit weights reflect)))

`(orbit-with-eps ,
  (lambda (self weights)
    (send self 'general-orbit weights reflect-with-eps)))
\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{20}\nwdocspar
\begin{Def}
  {\bf Fundamental weights} form a basis $w_1,\dots,w_r$ dual to the basis of simple co-roots $\alpha_1^{\vee},\dots,\alpha_r^{\vee}$.
\end{Def}
\nwenddocs{}\nwbegincode{21}\sublabel{NW1VK18x-1H68wy-4}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-4}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-3}{NW1VK18x-1H68wy-5}\nwenddeflinemarkup
`(fundamental-weights
  ,(lambda (self)
     (map (lambda (x)
            (sum (map-n (lambda (y z) (mul y z)) x (send self 'simple-roots))))
          (matrix-inverse (send self 'cartan-matrix)))))
\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{22}\nwdocspar
{\bf Weyl vector} $\rho=\sum_i w_i=\frac{1}{2}\sum_{\alpha\in \Delta^{+}}\alpha$.
\nwenddocs{}\nwbegincode{23}\sublabel{NW1VK18x-1H68wy-5}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-5}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-4}{NW1VK18x-1H68wy-6}\nwenddeflinemarkup
`(rho ,(lambda (self)
         (sum (send self 'fundamental-weights))))

@@

\nwenddocs{}\nwbegincode{31}\sublabel{NW1VK18x-2w9Axe-2}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-2}}}\moddef{Representations .scm~{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwprevnextdefs{NW1VK18x-2w9Axe-1}{\relax}\nwenddeflinemarkup
(class 'highest-weight-representation 'representation
       '(highest-weight ())
       \LA{}Anomalous weights computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}\RA{}
       \LA{}Weight multiplicities computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}\RA{})
\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{32}\nwdocspar
We use the recurrent method of calculation of weight multiplicities described in \cite{lyakhovsky1996rra}, \cite{kulish4sfa}. Weight multiplicities are determined using the set of anomalous points, which is constructed by the code below.
We use the recurrent relation
\begin{equation}
  m_{\xi }^{\left( \mu \right) }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
-\left( w\cdot\rho-\rho \right) }^{\left( \mu \right) }+\sum_{w\in W}\epsilon
(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.  \label{gen-mult-form}
\end{equation}
The second term on the right-hand side is constructed with the code:
\nwenddocs{}\nwbegincode{33}\sublabel{NW1VK18x-1y2eh2-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}}\moddef{Anomalous weights computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2w9Axe-2}}\nwenddeflinemarkup
       `(anomalous-weights , 
         (lambda (self)
           (let* ((algebra (send self 'lie-algebra))
                  (rho (send algebra 'rho)))
             (map (lambda (x)
                    (sub x rho))
                  (send algebra 'orbit (add (send self 'highest-weight) rho))))))
\nwused{\\{NW1VK18x-2w9Axe-2}}\nwendcode{}\nwbegindocs{34}\nwdocspar
Then multiplicity of the weight $\xi$ is calculated as the sum over the set $\omega\rho-\rho$, which we call ``star''

\nwenddocs{}\nwbegincode{35}\sublabel{NW1VK18x-46EOV9-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}}\moddef{Weight multiplicities computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2w9Axe-2}}\nwenddeflinemarkup
`(multiplicity , (lambda (self weight)
                   (let ((star \LA{}Construct star .scm~{\nwtagstyle{}\subpageref{nw@notdef}}\RA{}))
                     (-
                      (sum (map (lambda (wg) (* (eps wg) (delta weight wg)))))
                      (sum (map (lambda (wg)
                                    (* (eps wg)
                                       (send self 'multiplicity (sub weight wg))))
                                  star))))))

@@

\nwused{\\{NW1VK18x-2tcrGt-1}}\nwendcode{}\nwbegindocs{53}\nwdocspar

\subsection{Supplementary mathematical functions}
\label{sec:suppl-math-funct}

\nwenddocs{}\nwbegincode{54}\sublabel{NW1VK18x-1tnUC5-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1tnUC5-1}}}\moddef{Supplementary math .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1tnUC5-1}}}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup

(define (delta weight1 weight2)
  (equal? (no-eps weight1) (no-eps weight2)))
\nwnotused{Supplementary math .scm}\nwendcode{}

\nwixlogsorted{c}{{Anomalous weights computation .scm}{NW1VK18x-1y2eh2-1}{\nwixu{NW1VK18x-2w9Axe-2}\nwixd{NW1VK18x-1y2eh2-1}}}%
\nwixlogsorted{c}{{Commutative algebra .scm}{NW1VK18x-I1QOi-1}{\nwixd{NW1VK18x-I1QOi-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Construct star .scm}{nw@notdef}{\nwixu{NW1VK18x-46EOV9-1}}}%
\nwixlogsorted{c}{{Functions for root systems .scm}{NW1VK18x-10zTlp-1}{\nwixd{NW1VK18x-10zTlp-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{library.scm}{NW1VK18x-15DMjX-1}{\nwixd{NW1VK18x-15DMjX-1}}}%
\nwixlogsorted{c}{{Lie algebra class .scm}{NW1VK18x-4dzmez-1}{\nwixd{NW1VK18x-4dzmez-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Lie algebra methods .scm}{NW1VK18x-4X6QTQ-1}{\nwixu{NW1VK18x-4dzmez-1}\nwixd{NW1VK18x-4X6QTQ-1}}}%
\nwixlogsorted{c}{{lie-algebra.scm}{NW1VK18x-3yKaW-1}{\nwixd{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{LispMe Objects .scm}{NW1VK18x-26RKW4-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-26RKW4-1}}}%
\nwixlogsorted{c}{{Matrix inverse .scm}{NW1VK18x-1qnsIb-1}{\nwixu{NW1VK18x-2tcrGt-1}\nwixd{NW1VK18x-1qnsIb-1}}}%
\nwixlogsorted{c}{{Representations .scm}{NW1VK18x-2w9Axe-1}{\nwixd{NW1VK18x-2w9Axe-1}\nwixd{NW1VK18x-2w9Axe-2}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Root system methods .scm}{NW1VK18x-1H68wy-1}{\nwixu{NW1VK18x-1pDr9o-1}\nwixd{NW1VK18x-1H68wy-1}\nwixd{NW1VK18x-1H68wy-2}\nwixd{NW1VK18x-1H68wy-3}\nwixd{NW1VK18x-1H68wy-4}\nwixd{NW1VK18x-1H68wy-5}\nwixd{NW1VK18x-1H68wy-6}}}%
\nwixlogsorted{c}{{Semi-standard Scheme procedures .scm}{NW1VK18x-16zbNk-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-16zbNk-1}}}%
\nwixlogsorted{c}{{Semisimple Lie algebra .scm}{NW1VK18x-1QMleH-1}{\nwixd{NW1VK18x-1QMleH-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Semisimple Lie algebra methods .scm}{NW1VK18x-1pDr9o-1}{\nwixu{NW1VK18x-1QMleH-1}\nwixd{NW1VK18x-1pDr9o-1}}}%
\nwixlogsorted{c}{{Sets .scm}{NW1VK18x-3j9Egk-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-3j9Egk-1}}}%
\nwixlogsorted{c}{{Simple Lie algebras .scm}{NW1VK18x-379yCw-1}{\nwixd{NW1VK18x-379yCw-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Supplementary math .scm}{NW1VK18x-1tnUC5-1}{\nwixd{NW1VK18x-1tnUC5-1}}}%
\nwixlogsorted{c}{{Vector and matrix tools .scm}{NW1VK18x-2tcrGt-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-2tcrGt-1}}}%
\nwixlogsorted{c}{{Vector operations .scm}{NW1VK18x-14pT7v-1}{\nwixu{NW1VK18x-2tcrGt-1}\nwixd{NW1VK18x-14pT7v-1}}}%
\nwixlogsorted{c}{{Weight multiplicities computation .scm}{NW1VK18x-46EOV9-1}{\nwixu{NW1VK18x-2w9Axe-2}\nwixd{NW1VK18x-46EOV9-1}}}%
\nwbegindocs{55}\nwdocspar
\bibliography{LiterateLie}{}
\bibliographystyle{utphys}
